% !TEX root = ../main.tex

\input{tables/table1}
\input{tables/table2}
\input{tables/table3}

\section{Code audit}\label{sec:tools}

We used a variety of code audit tools on \sys to validate the code and also to illuminate the completeness and error-rate of such tools on one specific use-case (similar work studies in less depth a variety of use-cases\cite{AuditTools}). We also did not adapt older tools that support significantly lower versions of the Solidity compiler (\eg Oyente). {\blue Moreover, if the version of tool is not mentioned, online versions are used which do not have a specific version}:
\begin{enumerate}[noitemsep,topsep=0pt]
	\item EY Review Tool by Ernst \& Young Global Limited\cite{EYTool}.
	\item SmartCheck by SmartDec\cite{SMARTCHECK}.
	\item Securify v2.0 by ChainSecurity\cite{SECURIFY}.
	\item ContractGuard by GuardStrike\cite{ContractGuard}.
	\item MythX by ConsenSys\cite{MythX}.
	\item Slither Analyzer v0.6.12 by Crytic\cite{SlitherDoc}.
	\item Odin by Sooho\cite{Odin}.
\end{enumerate}

\subsection{Analysis of audit results}
A total of \num audits have been conducted by these auditing tools. Audits include best practices and security vulnerabilities. The results are summarized in Tables\ref{tab:result1}--\ref{tab:result3}. To compile the list, we referenced the knowledge-base of each tool\cite{SECURIFYGIT,SMARTCHECK,MythX,ContractGuard,SlitherDoc}, understood each threat, manually mapped the audit to the corresponding SWC registry\cite{SWC}, and manually determined when different tools were testing for the same vulnerability or best practice (which was not always clear from the tools' own descriptions). Space will not permit us to discuss each one at the same level of detail as the ones we highlight in sections \ref{sec:vul} and \ref{sec:bp}, however we will include a simple statement describing the issue and the mitigation.

Since each tool employs different methodology to analyze smart contracts (\eg comparing with violation patterns, applying a set of rules, using static analysis, \etc), there are false positives to manually check. {\blue Some false positive (\eg \textit{noReentrancy} modifier in \textit{MythX} and \textit{ContractGuard}) are not due to old/unmaintained rules. There is a need to optimize the tools to consider \texttt{Modifiers} in code analysis.}  The following are some examples of false positives (which we do not count in calculating our success rate):
\begin{enumerate}[noitemsep,topsep=0pt]
	\item \textit{MythX} detects \textit{Re-entrancy attack} in the \textit{noReentrancy} modifier. In Solidity, modifiers are not like functions. They are used to add features or apply some restriction on functions\cite{SolidityModifer}. Using modifiers is a known technique to implement Mutex and mitigate the attack\cite{ReentrancyGuard}. This is a false positive and note that other tools have not identified the attack in modifiers.

	\item \textit{ContractGuard} flags \textit{Re-entrancy attack} in \texttt{transfer()} function while both CEI and Mutex are implemented.

	\item \textit{Slither} detects two \textit{low level call} vulnerabilities\cite{SlitherSetup}. This is due to use of \texttt{call.value()} that is recommend way of transferring ETH after \textit{Istanbul} hard-fork (EIP-1884).	Therefore, adapting analyzers to new standards can improve accuracy of the security checks.

	\item \textit{SmartCheck} recommends not using \texttt{SafeMath} and check explicitly where overflows might be occurred. We consider this failed audit as false possible whereas utilizing \texttt{SafeMath} is a known technique to mitigate over/under flows. It also flags \textit{using a private modifier} as a vulnerability by mentioning, ``miners have access to all contracts' data and developers must account for the lack of privacy in Ethereum''. However private visibility in Solidity concerns object oriented inheritance not confidentiality. For actual confidentiality, the best practice is to encrypt private data or store them off-chain. The tool also warns against \texttt{approve()} in \erc due to \textit{front-running attacks}. Despite EIP-1884, it still recommends using of \texttt{transfer()} method with stipend of 2300 gas. There are other false positives such as SWC-105 and SWC-112 that are passed by other tools.

	\item \textit{Securify} detects the \textit{Re-entrancy} attack due to unrestricted writes in the \texttt{noReentrancy} modifier\cite{SECURIFY}. Modifiers are the recommended approach and are not accessible by users. It also flags \textit{Delegatecall to Untrusted Callee (SWC-112)} while there is no usage of \texttt{delegatecall()} in the code. It might be due to use of \texttt{SafeMath} library which is an embedded library. In Solidity, embedded libraries are called by JUMP commands instead of \texttt{delegatecall()}. Therefore, excluding embedded libraries from this check might improve accuracy of the tool. Similar to \textit{SmartCheck}, it still recommends to use the \texttt{transfer()} method instead of \texttt{call.value()}.

	\item \textit{EY token review} considers \texttt{decreaseAllowance} and \texttt{increaseAllowance} as standard \erc functions and if not implemented, recognizes the code as vulnerable to a \textit{front-running}. These two functions are not defined in the \erc standard\cite{ERC20Std} and considered only by this tool as mandatory functions. There are other methods to prevent the attack while adhering \erc specifications (see Rahimian \etal for a full paper on this attack and the basis of the mitigation in \sys\cite{ERC20MWA}). The tool also falsely detects the \textit{Overflow}, mitigated through \texttt{SafeMath}. Another identified issue is \textit{Funds can be held only by user-controlled wallets}. The tool warns against any token transfer to Ethereum addresses that belong to smart contracts. However, interacting with \erc token by other smart contracts was one of the main motivations of the standard. It also checks for maximum 50000 gas in \texttt{approve()} and 60000 in \texttt{transfer()} method. We could not find corresponding SWC registry or standard recommendation on these limitations and therefore consider them as informational.

	\item \textit{Odin} raises \textit{Outdated compiler version} issue due to locking solidity version to 0.5.11. We have used this version due to its compatibility with other auditing tools. Furthermore, other tools have not identified such an issue and we therefore consider it as informational.
\end{enumerate}

%(1) EY Review Tool by Ernst \& Young Global Limited\cite{EYTool}, (2) SmartCheck by SmartDec\cite{SMARTCHECK}, (3) Securify v2.0 by ChainSecurity\cite{SECURIFY}, (4) ContractGuard by GuardStrike\cite{ContractGuard}, (5) MythX by ConsenSys\cite{MythX}, (6) Slither Analyzer by Crytic\cite{SlitherDoc} and (7) Odin by Sooho\cite{Odin}.
%(this is more applicable to smart contracts than \erc tokens)